### 2017-08-21 paper/incomeShocks-jde-r1.tex
Add log croploss results to Appendix
Add continuous loss measure table to appendix

% Log of crop loss
\caption{The Effects of Log Crop Loss}
\label{tab:ln_croploss}
 & \multicolumn{5}{c}{Without interaction with assets} \\
Log crop loss - 1-7 months                             &      -0.102\sym{*}  &                     &       0.322\sym{***}&       0.333\sym{***}&      -0.013         \\
                                                       &     (0.060)         &                     &     (0.062)         &     (0.060)         &     (0.025)         \\
Log crop loss - 7-14 months                            &                     &      -0.119\sym{*}  &                     &                     &                     \\
                                                       &                     &     (0.061)         &                     &                     &                     \\
 & \multicolumn{5}{c}{With interaction with assets} \\
Log crop loss - 1-7 months                             &      -0.135\sym{*}  &                     &       0.360\sym{***}&       0.353\sym{***}&       0.012         \\
                                                       &     (0.070)         &                     &     (0.086)         &     (0.083)         &     (0.023)         \\
Log crop loss - 1-7 months                             &       0.002\sym{*}  &                     &      -0.002         &      -0.001         &      -0.002         \\
\hs \X initial assets (10,000 TZS)                     &     (0.001)         &                     &     (0.005)         &     (0.004)         &     (0.001)         \\
Log crop loss - 7-14 months                            &                     &      -0.149\sym{**} &                     &                     &                     \\
                                                       &                     &     (0.075)         &                     &                     &                     \\
Log crop loss - 7-14 months                            &                     &       0.002         &                     &                     &                     \\
\hs \X initial assets (10,000 TZS)                     &                     &     (0.002)         &                     &                     &                     \\
 & \multicolumn{5}{c}{With interaction with log assets} \\
Log crop loss - 1-7 months                             &      -0.401         &                     &       1.684\sym{***}&       1.518\sym{**} &       0.283\sym{*}  \\
                                                       &     (0.278)         &                     &     (0.601)         &     (0.597)         &     (0.145)         \\
Log crop loss - 1-7 months                             &       0.027         &                     &      -0.122\sym{**} &      -0.106\sym{*}  &      -0.027\sym{*}  \\
\hs \X log initial assets (10,000 TZS)                 &     (0.025)         &                     &     (0.056)         &     (0.056)         &     (0.014)         \\
Log crop loss - 7-14 months                            &                     &      -0.469         &                     &                     &                     \\
                                                       &                     &     (0.309)         &                     &                     &                     \\
Log crop loss - 7-14 months                            &                     &       0.031         &                     &                     &                     \\
\hs \X log initial assets (10,000 TZS)                 &                     &     (0.026)         &                     &                     &                     \\
Crop loss is log per capita crop loss plus 1.
Assets are assets per capita in round 1 of the survey and are measured in 10,000 TZS.
Log of assets are taken off assets per capita in TZS.

% Linear crop loss

\begin{table}[htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{The Effects of Crop Loss Using Continuous Measure}
\label{tab:continuous}
\begin{tabular}{@{} l D{.}{.}{2.6} D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6}  @{}}
\toprule
                                                       & \mco{}              &\mco{}               &\multicolumn{3}{c}{Contraceptive Use}\\ \cmidrule(lr){4-6}
                                                       & \mco{Pregnant}      &\mco{Birth}          &\mco{Any}            &\mco{Traditional}    & \mco{Modern}        \\ \midrule
 & \multicolumn{5}{c}{Without interaction with assets} \\
Crop loss - 1-7 months (10,000 TZS)                    &      -0.022         &                     &       0.102\sym{***}&       0.114\sym{***}&      -0.013         \\
                                                       &     (0.018)         &                     &     (0.030)         &     (0.023)         &     (0.008)         \\
Crop loss - 7-14 months (10,000 TZS)                   &                     &      -0.023         &                     &                     &                     \\
                                                       &                     &     (0.017)         &                     &                     &                     \\
\addlinespace 
 & \multicolumn{5}{c}{With interaction with assets} \\
Crop loss - 1-7 months (10,000 TZS)                    &      -0.041\sym{*}  &                     &       0.124\sym{***}&       0.127\sym{***}&      -0.003         \\
                                                       &     (0.024)         &                     &     (0.038)         &     (0.033)         &     (0.008)         \\
Crop loss - 1-7 months                                 &       0.001         &                     &      -0.001         &      -0.001         &      -0.001         \\
\hs \X initial assets (10,000 TZS)                     &     (0.001)         &                     &     (0.002)         &     (0.002)         &     (0.000)         \\
Crop loss - 7-14 months (10,000 TZS)                   &                     &      -0.039         &                     &                     &                     \\
                                                       &                     &     (0.025)         &                     &                     &                     \\
Crop loss - 7-14 months                                &                     &       0.001         &                     &                     &                     \\
\hs \X initial assets (10,000 TZS)                     &                     &     (0.001)         &                     &                     &                     \\
\addlinespace 
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{741}        &    \mco{988}        &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a per capita crop loss and measured in 10,000 TZS.
Assets are assets per capita in round 1 of the survey and are measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

>>>>

% Log of crop loss
\input{../tables/appendix_log_croploss.tex}

% Linear crop loss
\input{../tables/appendix_cont_croploss.tex}
